---
title: "My R Codes 2"
author: "Sedi Abbasnasab"
date: '11.10.2022'
output: html_document
---

# Import my data
```{r}
mydata <- read.csv(file.choose())
```
# Install ggplot2
```{r}
install.packages("ggplot2")
```
# Scatter plot for mydata
```{r}
ggplot(data=mydata[mydata$carat<2.5,], 
       aes(x=carat, y=price, colour = clarity)) + 
  geom_point(alpha=0.1) +
  geom_smooth()
```

# Using variables in R
```{r}
A <- 10
B <- 5
C <- A + B
C
```
```{r}
var1 <- 2.5
var2 <- 4
result <- var1 / var2
result
answer <- sqrt(var2)
answer
```
```{r}
greeting <- "Hello"
name <- "Bob"
message <- paste(greeting, name)
message
```

# Sample logical variables and operators
```{r}
4 < 5
result <- 4 < 5
typeof(result)
```
```{r}
result2 <- ! TRUE
result2
```
```{r}
result | result2
```
```{r}
result & result2
```
```{r}
isTRUE(result)
```

# The While loop
```{r}
counter <- 1
while(counter < 12){
  print(counter)
  counter <- counter + 1
}
```

# The for loop
```{r}
for(i in 1:5){
  print("Hello R")
}
```
```{r}
for(i in 5:10){
  print("Hello R")
}
```

# The if statement
```{r}
rm(answer)
x <- rnorm(1)
if(x > 1){
  answer <- "Greater than 1"
} else if(x >= -1){
      answer <- "Between -1 and 1"
    } else{
        answer <- "Less than -1"
      }
```

# The law of large numbers
```{r}
N <- 10000000 # input
counter <- 0 #reset counter
for(i in rnorm(N)){ # iterate over vector of numbers
  if(i > -1 & i < 1){ # check where iterated variable falls
    counter <- counter + 1 # increase counter if condition is met
  }
}
counter / N # calculate hit ratio
```

# Vector
```{r}
vector <- c(3, 45, 56, 732)
vector
is.numeric(vector)
is.integer(vector)
is.double(vector)
```
```{r}
V2 <- c(3L, 12L, 243L, 0L)
V2
is.numeric(V2)
is.integer(V2)
is.double(V2)
```
```{r}
V3 <- c("a", "B23", "Hello")
V3
is.character(V3)
is.numeric(V3)
```

# Sequence vs column
```{r}
seq(1,15)
1:15
seq(1,15,2)
z <- seq(1,15,4)
z
```

# Replicate
```{r}
rep(3, 100)
d <- rep(3, 50)
rep("a", 5)

x <- c(80, 20)
y <- rep(x,10)
y

```

# Brackets
```{r}
w <- c("a", "b", "c", "d", "e")
w
w[1]
w[2]
w[3]
w[-1]
v <- w[-3]
v
w[1:3]
w[3:5]
w[c(1,3,5)]
w[c(-2,-4)]
w[-3:-5]

```

#Vectorized operations
```{r}
# R-specific programming loop
x <- rnorm(5)
x
for(i in x){
  print(i)
}

print(x[1])
print(x[2])
print(x[3])
print(x[4])
print(x[5])

# conventional programming loop
for(j in 1:5){
  print(x[j])
}
# vectorized vs devectorized operations
N <- 100
a <- rnorm(N)
b <- rnorm(N)
# vectorized
c <- a * b
#devectorized
d <- rep(NA,N)
for(i in 1:N){
  d[i] <- a[i] * b[i]
}

```

# Analyzing financial statements
```{r}
#Data
revenue <- c(14574.49, 7606.46, 8611.41, 9175.41, 8058.65, 8105.44, 11496.28, 9766.09, 10305.32, 14379.96, 10713.97, 15433.50)
expenses <- c(12051.82, 5695.07, 12319.20, 12089.72, 8658.57, 840.20, 3285.73, 5821.12, 6976.93, 16618.61, 10054.37, 3803.96)

#Solution
#Calculate Profit As The Differences Between Revenue And Expenses
profit <- revenue - expenses
profit

#Calculate Tax As 30% Of Profit And Round To 2 Decimal Points
tax <- round(0.30 * profit, 2)
tax 

#Calculate Profit Remaining After Tax Is Deducted
profit.after.tax <- profit - tax
profit.after.tax

#Calculate The Profit Margin As Profit After Tax Over Revenue
#Round To 2 Decimal Points, Then Multiply By 100 To Get %
profit.margin <- round(profit.after.tax / revenue, 2) * 100
profit.margin

#Calculate The Mean Profit After Tax For The 12 Months
mean_pat <- mean(profit.after.tax)
mean_pat

#Find The Months With Above-Mean Profit After Tax
good.months <- profit.after.tax > mean_pat
good.months

#Bad Months Are The Opposite Of Good Months !
bad.months <- !good.months
bad.months

#The Best Month Is Where Profit After Tax Was Equal To The Maximum
best.month <- profit.after.tax == max(profit.after.tax)
best.month

#The Worst Month Is Where Profit After Tax Was Equal To The Minimum
worst.month <- profit.after.tax == min(profit.after.tax)
worst.month

#Convert All Calculations To Units Of One Thousand Dollars
revenue.1000 <- round(revenue / 1000)
expenses.1000 <- round(expenses / 1000)
profit.1000 <- round(profit / 1000)
profit.after.tax.1000 <- round(profit.after.tax / 1000)

#Print Results
revenue.1000
expenses.1000
profit.1000
profit.after.tax.1000
profit.margin
good.months
bad.months
best.month
worst.month

#BONUS:
#Preview Of What's Coming In The Next Section
M <- rbind(
  revenue.1000,
  expenses.1000,
  profit.1000,
  profit.after.tax.1000,
  profit.margin,
  good.months,
  bad.months,
  best.month,
  worst.month
)

#Print The Matrix
M

```


# The world of Basketball Data!

#Instructions for this dataset:
# Simply select ALL the lines in this script by pressing 
# CTRL+A on Windows or CMND+A on a Mac and execute them
# Once you have executed the commands the following objects
# will be created:
# Matrices:
# - FieldGoalAttempts
# - FieldGoals
# - Games
# - MinutesPlayed
# - Salary
# Vectors:
# - Players
# - Seasons


#Comments:
#Seasons are labeled based on the first year in the season
#E.g. the 2012-2013 season is preseneted as simply 2012


# Seasons
```{r}
Seasons <- c("2005","2006","2007","2008","2009","2010","2011","2012","2013","2014")
```

# Players
```{r}
Players <- c("KobeBryant","JoeJohnson","LeBronJames","CarmeloAnthony","DwightHoward","ChrisBosh","ChrisPaul","KevinDurant","DerrickRose","DwayneWade")
```

# Salaries
```{r}
KobeBryant_Salary <- c(15946875,17718750,19490625,21262500,23034375,24806250,25244493,27849149,30453805,23500000)
JoeJohnson_Salary <- c(12000000,12744189,13488377,14232567,14976754,16324500,18038573,19752645,21466718,23180790)
LeBronJames_Salary <- c(4621800,5828090,13041250,14410581,15779912,14500000,16022500,17545000,19067500,20644400)
CarmeloAnthony_Salary <- c(3713640,4694041,13041250,14410581,15779912,17149243,18518574,19450000,22407474,22458000)
DwightHoward_Salary <- c(4493160,4806720,6061274,13758000,15202590,16647180,18091770,19536360,20513178,21436271)
ChrisBosh_Salary <- c(3348000,4235220,12455000,14410581,15779912,14500000,16022500,17545000,19067500,20644400)
ChrisPaul_Salary <- c(3144240,3380160,3615960,4574189,13520500,14940153,16359805,17779458,18668431,20068563)
KevinDurant_Salary <- c(0,0,4171200,4484040,4796880,6053663,15506632,16669630,17832627,18995624)
DerrickRose_Salary <- c(0,0,0,4822800,5184480,5546160,6993708,16402500,17632688,18862875)
DwayneWade_Salary <- c(3031920,3841443,13041250,14410581,15779912,14200000,15691000,17182000,18673000,15000000)
```

# Matrix
```{r}
Salary <- rbind(KobeBryant_Salary, JoeJohnson_Salary, LeBronJames_Salary, CarmeloAnthony_Salary, DwightHoward_Salary, ChrisBosh_Salary, ChrisPaul_Salary, KevinDurant_Salary, DerrickRose_Salary, DwayneWade_Salary)
rm(KobeBryant_Salary, JoeJohnson_Salary, CarmeloAnthony_Salary, DwightHoward_Salary, ChrisBosh_Salary, LeBronJames_Salary, ChrisPaul_Salary, DerrickRose_Salary, DwayneWade_Salary, KevinDurant_Salary)
colnames(Salary) <- Seasons
rownames(Salary) <- Players
```

# Games
```{r}
KobeBryant_G <- c(80,77,82,82,73,82,58,78,6,35)
JoeJohnson_G <- c(82,57,82,79,76,72,60,72,79,80)
LeBronJames_G <- c(79,78,75,81,76,79,62,76,77,69)
CarmeloAnthony_G <- c(80,65,77,66,69,77,55,67,77,40)
DwightHoward_G <- c(82,82,82,79,82,78,54,76,71,41)
ChrisBosh_G <- c(70,69,67,77,70,77,57,74,79,44)
ChrisPaul_G <- c(78,64,80,78,45,80,60,70,62,82)
KevinDurant_G <- c(35,35,80,74,82,78,66,81,81,27)
DerrickRose_G <- c(40,40,40,81,78,81,39,0,10,51)
DwayneWade_G <- c(75,51,51,79,77,76,49,69,54,62)
```

# Matrix
```{r}
Games <- rbind(KobeBryant_G, JoeJohnson_G, LeBronJames_G, CarmeloAnthony_G, DwightHoward_G, ChrisBosh_G, ChrisPaul_G, KevinDurant_G, DerrickRose_G, DwayneWade_G)
rm(KobeBryant_G, JoeJohnson_G, CarmeloAnthony_G, DwightHoward_G, ChrisBosh_G, LeBronJames_G, ChrisPaul_G, DerrickRose_G, DwayneWade_G, KevinDurant_G)
colnames(Games) <- Seasons
rownames(Games) <- Players
```

# Minutes Played
```{r}
KobeBryant_MP <- c(3277,3140,3192,2960,2835,2779,2232,3013,177,1207)
JoeJohnson_MP <- c(3340,2359,3343,3124,2886,2554,2127,2642,2575,2791)
LeBronJames_MP <- c(3361,3190,3027,3054,2966,3063,2326,2877,2902,2493)
CarmeloAnthony_MP <- c(2941,2486,2806,2277,2634,2751,1876,2482,2982,1428)
DwightHoward_MP <- c(3021,3023,3088,2821,2843,2935,2070,2722,2396,1223)
ChrisBosh_MP <- c(2751,2658,2425,2928,2526,2795,2007,2454,2531,1556)
ChrisPaul_MP <- c(2808,2353,3006,3002,1712,2880,2181,2335,2171,2857)
KevinDurant_MP <- c(1255,1255,2768,2885,3239,3038,2546,3119,3122,913)
DerrickRose_MP <- c(1168,1168,1168,3000,2871,3026,1375,0,311,1530)
DwayneWade_MP <- c(2892,1931,1954,3048,2792,2823,1625,2391,1775,1971)
```

# Matrix
```{r}
MinutesPlayed <- rbind(KobeBryant_MP, JoeJohnson_MP, LeBronJames_MP, CarmeloAnthony_MP, DwightHoward_MP, ChrisBosh_MP, ChrisPaul_MP, KevinDurant_MP, DerrickRose_MP, DwayneWade_MP)
rm(KobeBryant_MP, JoeJohnson_MP, CarmeloAnthony_MP, DwightHoward_MP, ChrisBosh_MP, LeBronJames_MP, ChrisPaul_MP, DerrickRose_MP, DwayneWade_MP, KevinDurant_MP)
colnames(MinutesPlayed) <- Seasons
rownames(MinutesPlayed) <- Players
```

# Field Goals
```{r}
KobeBryant_FG <- c(978,813,775,800,716,740,574,738,31,266)
JoeJohnson_FG <- c(632,536,647,620,635,514,423,445,462,446)
LeBronJames_FG <- c(875,772,794,789,768,758,621,765,767,624)
CarmeloAnthony_FG <- c(756,691,728,535,688,684,441,669,743,358)
DwightHoward_FG <- c(468,526,583,560,510,619,416,470,473,251)
ChrisBosh_FG <- c(549,543,507,615,600,524,393,485,492,343)
ChrisPaul_FG <- c(407,381,630,631,314,430,425,412,406,568)
KevinDurant_FG <- c(306,306,587,661,794,711,643,731,849,238)
DerrickRose_FG <- c(208,208,208,574,672,711,302,0,58,338)
DwayneWade_FG <- c(699,472,439,854,719,692,416,569,415,509)
```

# Matrix
```{r}
FieldGoals <- rbind(KobeBryant_FG, JoeJohnson_FG, LeBronJames_FG, CarmeloAnthony_FG, DwightHoward_FG, ChrisBosh_FG, ChrisPaul_FG, KevinDurant_FG, DerrickRose_FG, DwayneWade_FG)
rm(KobeBryant_FG, JoeJohnson_FG, LeBronJames_FG, CarmeloAnthony_FG, DwightHoward_FG, ChrisBosh_FG, ChrisPaul_FG, KevinDurant_FG, DerrickRose_FG, DwayneWade_FG)
colnames(FieldGoals) <- Seasons
rownames(FieldGoals) <- Players
```

# Field Goal Attempts
```{r}
KobeBryant_FGA <- c(2173,1757,1690,1712,1569,1639,1336,1595,73,713)
JoeJohnson_FGA <- c(1395,1139,1497,1420,1386,1161,931,1052,1018,1025)
LeBronJames_FGA <- c(1823,1621,1642,1613,1528,1485,1169,1354,1353,1279)
CarmeloAnthony_FGA <- c(1572,1453,1481,1207,1502,1503,1025,1489,1643,806)
DwightHoward_FGA <- c(881,873,974,979,834,1044,726,813,800,423)
ChrisBosh_FGA <- c(1087,1094,1027,1263,1158,1056,807,907,953,745)
ChrisPaul_FGA <- c(947,871,1291,1255,637,928,890,856,870,1170)
KevinDurant_FGA <- c(647,647,1366,1390,1668,1538,1297,1433,1688,467)
DerrickRose_FGA <- c(436,436,436,1208,1373,1597,695,0,164,835)
DwayneWade_FGA <- c(1413,962,937,1739,1511,1384,837,1093,761,1084)
```

# Matrix
```{r}
FieldGoalAttempts <- rbind(KobeBryant_FGA, JoeJohnson_FGA, LeBronJames_FGA, CarmeloAnthony_FGA, DwightHoward_FGA, ChrisBosh_FGA, ChrisPaul_FGA, KevinDurant_FGA, DerrickRose_FGA, DwayneWade_FGA)
rm(KobeBryant_FGA, JoeJohnson_FGA, LeBronJames_FGA, CarmeloAnthony_FGA, DwightHoward_FGA, ChrisBosh_FGA, ChrisPaul_FGA, KevinDurant_FGA, DerrickRose_FGA, DwayneWade_FGA)
colnames(FieldGoalAttempts) <- Seasons
rownames(FieldGoalAttempts) <- Players
```

# Points
```{r}
KobeBryant_PTS <- c(2832,2430,2323,2201,1970,2078,1616,2133,83,782)
JoeJohnson_PTS <- c(1653,1426,1779,1688,1619,1312,1129,1170,1245,1154)
LeBronJames_PTS <- c(2478,2132,2250,2304,2258,2111,1683,2036,2089,1743)
CarmeloAnthony_PTS <- c(2122,1881,1978,1504,1943,1970,1245,1920,2112,966)
DwightHoward_PTS <- c(1292,1443,1695,1624,1503,1784,1113,1296,1297,646)
ChrisBosh_PTS <- c(1572,1561,1496,1746,1678,1438,1025,1232,1281,928)
ChrisPaul_PTS <- c(1258,1104,1684,1781,841,1268,1189,1186,1185,1564)
KevinDurant_PTS <- c(903,903,1624,1871,2472,2161,1850,2280,2593,686)
DerrickRose_PTS <- c(597,597,597,1361,1619,2026,852,0,159,904)
DwayneWade_PTS <- c(2040,1397,1254,2386,2045,1941,1082,1463,1028,1331)
```

# Matrix
```{r}
Points <- rbind(KobeBryant_PTS, JoeJohnson_PTS, LeBronJames_PTS, CarmeloAnthony_PTS, DwightHoward_PTS, ChrisBosh_PTS, ChrisPaul_PTS, KevinDurant_PTS, DerrickRose_PTS, DwayneWade_PTS)
rm(KobeBryant_PTS, JoeJohnson_PTS, LeBronJames_PTS, CarmeloAnthony_PTS, DwightHoward_PTS, ChrisBosh_PTS, ChrisPaul_PTS, KevinDurant_PTS, DerrickRose_PTS, DwayneWade_PTS)
colnames(Points) <- Seasons
rownames(Points) <- Players
```

# Matrix operations and visualizations basketball data
```{r}
Games
rownames(Games)
colnames(Games)
Games["LeBronJames", "2012"]

FieldGoals
round(FieldGoals / Games)
round(MinutesPlayed / Games)
round(FieldGoalAttempts / Games)
round(FieldGoals / FieldGoalAttempts)


matplot(t(FieldGoals), type="b", pch = 15:18, col = c(1:4,6))
legend("bottomleft", inset = 0.01, legend = Players, col = c(1:4,6), pch = 15:18, horiz = FALSE)

matplot(t(FieldGoals/FieldGoalAttempts), type="b", pch = 15:18, col = c(1:4,6))
legend("bottomleft", inset = 0.01, legend = Players, col = c(1:4,6), pch = 15:18, horiz = FALSE)

matplot((Salary/Points), type="b", pch=15:18, col=c(1:4,6))
legend("bottomleft", inset = 0.01, legend = Players, col = c(1:4,6), pch = 15:18, horiz = FALSE)

Data <- MinutesPlayed[1:3,]
matplot(t(Data), type = "b", pch = 15:18, col = c(1:4,6))
legend("bottomleft", inset = 0.01, legend = Players[1:3], col = c(1:4,6), pch = 15:18)

Data <- MinutesPlayed[1,,drop=F]
matplot(t(Data), type = "b", pch = 15:18, col = c(1:4,6))
legend("bottomleft", inset = 0.01, legend = Players[1], col = c(1:4,6), pch = 15:18)

myplot <- function(rows){
  Data <- MinutesPlayed[rows,,drop=F]
matplot(t(Data), type = "b", pch = 15:18, col = c(1:4,6))
legend("bottomleft", inset = 0.01, legend = Players[rows], col = c(1:4,6), pch = 15:18)
}

myplot(1:5)

myplot <- function(data, rows=1:10){
  Data <- data[rows,,drop=F]
matplot(t(Data), type = "b", pch = 15:18, col = c(1:4,6))
legend("bottomleft", inset = 0.01, legend = Players[rows], col = c(1:4,6), pch = 15:18)
}

myplot(MinutesPlayed/Games, 3)
```

# Analysis/visualizations of basketball data
```{r}
# Salary
myplot(Salary)
myplot(Salary/Games)
myplot(Salary/FieldGoals)

# In-Game metrics
myplot(MinutesPlayed)
myplot(Points)

# In-Game metrics normalized
myplot(FieldGoals/Games)
myplot(FieldGoals/FieldGoalAttempts)
myplot(FieldGoalAttempts/Games)
myplot(Points/Games)

# Interesting observation
myplot(MinutesPlayed/Games)
myplot(Games)

# Time is valuable
myplot(FieldGoals/MinutesPlayed)

# Player style
myplot(Points/FieldGoals)
```

# Basketball free throw
```{r}
# Seasons
Seasons <- c("2005","2006","2007","2008","2009","2010","2011","2012","2013","2014")
```
```{r}
# Players
Players <- c("KobeBryant","JoeJohnson","LeBronJames","CarmeloAnthony","DwightHoward","ChrisBosh","ChrisPaul","KevinDurant","DerrickRose","DwayneWade")
```
```{r}
# Free throws
KobeBryant_FT <- c(696,667,623,483,439,483,381,525,18,196)
JoeJohnson_FT <- c(261,235,316,299,220,195,158,132,159,141)
LeBronJames_FT <- c(601,489,549,594,593,503,387,403,439,375)
CarmeloAnthony_FT <- c(573,459,464,371,508,507,295,425,459,189)
DwightHoward_FT <- c(356,390,529,504,483,546,281,355,349,143)
ChrisBosh_FT <- c(474,463,472,504,470,384,229,241,223,179)
ChrisPaul_FT <- c(394,292,332,455,161,337,260,286,295,289)
KevinDurant_FT <- c(209,209,391,452,756,594,431,679,703,146)
DerrickRose_FT <- c(146,146,146,197,259,476,194,0,27,152)
DwayneWade_FT <- c(629,432,354,590,534,494,235,308,189,284)
```
```{r}
#Matrix for Free Throws
#Bind the given vectors to form the matrix
FreeThrows <- rbind(KobeBryant_FT, JoeJohnson_FT, LeBronJames_FT, CarmeloAnthony_FT, DwightHoward_FT, ChrisBosh_FT, ChrisPaul_FT, KevinDurant_FT, DerrickRose_FT, DwayneWade_FT)
#Remove vectors - we don't need them anymore
rm(KobeBryant_FT, JoeJohnson_FT, CarmeloAnthony_FT, DwightHoward_FT, ChrisBosh_FT, LeBronJames_FT, ChrisPaul_FT, DerrickRose_FT, DwayneWade_FT, KevinDurant_FT)

#Rename the columns
colnames(FreeThrows) <- Seasons
#Rename the rows
rownames(FreeThrows) <- Players

#Check the matrix
FreeThrows

# Free throes attempts
KobeBryant_FTA <- c(819,768,742,564,541,583,451,626,21,241)
JoeJohnson_FTA <- c(330,314,379,362,269,243,186,161,195,176)
LeBronJames_FTA <- c(814,701,771,762,773,663,502,535,585,528)
CarmeloAnthony_FTA <- c(709,568,590,468,612,605,367,512,541,237)
DwightHoward_FTA <- c(598,666,897,849,816,916,572,721,638,271)
ChrisBosh_FTA <- c(581,590,559,617,590,471,279,302,272,232)
ChrisPaul_FTA <- c(465,357,390,524,190,384,302,323,345,321)
KevinDurant_FTA <- c(256,256,448,524,840,675,501,750,805,171)
DerrickRose_FTA <- c(205,205,205,250,338,555,239,0,32,187)
DwayneWade_FTA <- c(803,535,467,771,702,652,297,425,258,370)

#Matrix for Free Throw Attempts

#Bind the given vectors to form the matrix
FreeThrowAttempts <- rbind(KobeBryant_FTA, JoeJohnson_FTA, LeBronJames_FTA, CarmeloAnthony_FTA, DwightHoward_FTA, ChrisBosh_FTA, ChrisPaul_FTA, KevinDurant_FTA, DerrickRose_FTA, DwayneWade_FTA)
#Remove vectors - we don't need them anymore
rm(KobeBryant_FTA, JoeJohnson_FTA, CarmeloAnthony_FTA, DwightHoward_FTA, ChrisBosh_FTA, LeBronJames_FTA, ChrisPaul_FTA, DerrickRose_FTA, DwayneWade_FTA, KevinDurant_FTA)
#Rename the columns
colnames(FreeThrowAttempts) <- Seasons
#Rename the rows
rownames(FreeThrowAttempts) <- Players

#Check the matrix
FreeThrowAttempts

#Re-create the plotting function
myplot <- function(z, who=1:10) {
  matplot(t(z[who,,drop=F]), type="b", pch=15:18, col=c(1:4,6), main="Basketball Players Analysis")
  legend("bottomleft", inset=0.01, legend=Players[who], col=c(1:4,6), pch=15:18, horiz=F)
}

#Visualize the new matrices
myplot(FreeThrows)
myplot(FreeThrowAttempts)

#Part 1 - Free Throw Attempts Per Game 
#(You will need the Games matrix)
myplot(FreeThrowAttempts/Games)
#Notice how Chris Paul gets few attempts per game

#Part 2 - Free Throw Accuracy
myplot(FreeThrows/FreeThrowAttempts)
#And yet Chris Paul's accuracy is one of the highest
#Chances are his team would get more points if he had more FTA's
#Also notice that Dwight Howard's FT Accuracy is extremely poor
#compared to other players. If you recall, Dwight Howard's
#Field Goal Accuracy was exceptional:
myplot(FieldGoals/FieldGoalAttempts)
#How could this be? Why is there such a drastic difference?
#We will see just now...

#Part 3 - Player Style Patterns Excluding Free Throws
myplot((Points-FreeThrows)/FieldGoals)
#Because we have excluded free throws, this plot now shows us
#the true representation of player style change. We can verify
#that this is the case because all the marks without exception
#on this plot are between 2 and 3. That is because Field Goals
#can only be for either 2 points or 3 points.
#Insights:
#1. You can see how players' preference for 2 or 3 point shots
#   changes throughout their career. We can see that almost all
#   players in this dataset experiment with their style throughout
#   their careers. Perhaps, the most drastic change in style has
#   been experienced by Joe Johnson.
#2. There is one exception. You can see that one player has not
#   changed his style at all - almost always scoring only 2-pointers.
#   Who is this mystert player? It's Dwight Howard! 
#   Now that explains a lot. The reason that Dwight Howard's
#   Field Goal accuracy is so good is because he almost always
#   scores 2-pointers only. That means he can be close to the basket
#   or even in contact with it. Free throws, on the other hand require
#   the player to stand 15ft (4.57m) away from the hoop. That's 
#   probably why Dwight Howard's Free Throw Accuracy is poor.
```

# Data frames
```{r}
# Importing data
stats <- read.csv(file.choose())
stats

# Exploring data
nrow(stats)
ncol(stats)
head(stats, n=10)
tail(stats, n=10)
str(stats)
summary(stats)

# Using the $ sign
stats[3, 3]
stats[3, "Birth.rate"]
stats$Birth.rate[3]
stats[,"Birth.rate"]
levels(stats$Income.Group)

# Basic operations with a data frame
#subsetting
stats[1:10,]
is.data.frame(stats[1,])
is.data.frame(stats[,1])
stats[,1,drop(F)]

# Multplying colums
stats$Birth.rate * stats$Internet.users

# Add column
stats$Mycalc <- stats$Birth.rate * stats$Internet.users
stats

# Remove a column
stats$Mycalc <- NULL

# Filtering data frames
filter <- stats$Internet.users < 2
stats
stats[filter,]

stats[stats$Birth.rate > 40 & stats$Internet.users < 2,]
stats[stats$Income.Group == "High income",]
stats[stats$Country.Name == "Malta",]

# Qplots
library(ggplot2)
?qplot

qplot(data=stats, x=Internet.users)
qplot(data=stats, x=Income.Group, y=Birth.rate, size=I(3),
      colour=I("blue"))
qplot(data=stats, x=Income.Group, y=Birth.rate, geom = "boxplot")

qplot(data=stats, x=Internet.users, y=Birth.rate)
qplot(data=stats, x=Internet.users, y=Birth.rate, size=I(4), colour=I("red"))
qplot(data=stats, x=Internet.users, y=Birth.rate, colour=Income.Group, size=I(5))

# Scatter plot illustrating Birth Rate and Internet Usage statistics categorized by Countries' Regions
# Countries regions vectors
Countries_2012_Dataset <- c("Aruba","Afghanistan","Angola","Albania","United Arab Emirates","Argentina","Armenia","Antigua and Barbuda","Australia","Austria","Azerbaijan","Burundi","Belgium","Benin","Burkina Faso","Bangladesh","Bulgaria","Bahrain","Bahamas, The","Bosnia and Herzegovina","Belarus","Belize","Bermuda","Bolivia","Brazil","Barbados","Brunei Darussalam","Bhutan","Botswana","Central African Republic","Canada","Switzerland","Chile","China","Cote d'Ivoire","Cameroon","Congo, Rep.","Colombia","Comoros","Cabo Verde","Costa Rica","Cuba","Cayman Islands","Cyprus","Czech Republic","Germany","Djibouti","Denmark","Dominican Republic","Algeria","Ecuador","Egypt, Arab Rep.","Eritrea","Spain","Estonia","Ethiopia","Finland","Fiji","France","Micronesia, Fed. Sts.","Gabon","United Kingdom","Georgia","Ghana","Guinea","Gambia, The","Guinea-Bissau","Equatorial Guinea","Greece","Grenada","Greenland","Guatemala","Guam","Guyana","Hong Kong SAR, China","Honduras","Croatia","Haiti","Hungary","Indonesia","India","Ireland","Iran, Islamic Rep.","Iraq","Iceland","Israel","Italy","Jamaica","Jordan","Japan","Kazakhstan","Kenya","Kyrgyz Republic","Cambodia","Kiribati","Korea, Rep.","Kuwait","Lao PDR","Lebanon","Liberia","Libya","St. Lucia","Liechtenstein","Sri Lanka","Lesotho","Lithuania","Luxembourg","Latvia","Macao SAR, China","Morocco","Moldova","Madagascar","Maldives","Mexico","Macedonia, FYR","Mali","Malta","Myanmar","Montenegro","Mongolia","Mozambique","Mauritania","Mauritius","Malawi","Malaysia","Namibia","New Caledonia","Niger","Nigeria","Nicaragua","Netherlands","Norway","Nepal","New Zealand","Oman","Pakistan","Panama","Peru","Philippines","Papua New Guinea","Poland","Puerto Rico","Portugal","Paraguay","French Polynesia","Qatar","Romania","Russian Federation","Rwanda","Saudi Arabia","Sudan","Senegal","Singapore","Solomon Islands","Sierra Leone","El Salvador","Somalia","Serbia","South Sudan","Sao Tome and Principe","Suriname","Slovak Republic","Slovenia","Sweden","Swaziland","Seychelles","Syrian Arab Republic","Chad","Togo","Thailand","Tajikistan","Turkmenistan","Timor-Leste","Tonga","Trinidad and Tobago","Tunisia","Turkey","Tanzania","Uganda","Ukraine","Uruguay","United States","Uzbekistan","St. Vincent and the Grenadines","Venezuela, RB","Virgin Islands (U.S.)","Vietnam","Vanuatu","West Bank and Gaza","Samoa","Yemen, Rep.","South Africa","Congo, Dem. Rep.","Zambia","Zimbabwe")
Codes_2012_Dataset <- c("ABW","AFG","AGO","ALB","ARE","ARG","ARM","ATG","AUS","AUT","AZE","BDI","BEL","BEN","BFA","BGD","BGR","BHR","BHS","BIH","BLR","BLZ","BMU","BOL","BRA","BRB","BRN","BTN","BWA","CAF","CAN","CHE","CHL","CHN","CIV","CMR","COG","COL","COM","CPV","CRI","CUB","CYM","CYP","CZE","DEU","DJI","DNK","DOM","DZA","ECU","EGY","ERI","ESP","EST","ETH","FIN","FJI","FRA","FSM","GAB","GBR","GEO","GHA","GIN","GMB","GNB","GNQ","GRC","GRD","GRL","GTM","GUM","GUY","HKG","HND","HRV","HTI","HUN","IDN","IND","IRL","IRN","IRQ","ISL","ISR","ITA","JAM","JOR","JPN","KAZ","KEN","KGZ","KHM","KIR","KOR","KWT","LAO","LBN","LBR","LBY","LCA","LIE","LKA","LSO","LTU","LUX","LVA","MAC","MAR","MDA","MDG","MDV","MEX","MKD","MLI","MLT","MMR","MNE","MNG","MOZ","MRT","MUS","MWI","MYS","NAM","NCL","NER","NGA","NIC","NLD","NOR","NPL","NZL","OMN","PAK","PAN","PER","PHL","PNG","POL","PRI","PRT","PRY","PYF","QAT","ROU","RUS","RWA","SAU","SDN","SEN","SGP","SLB","SLE","SLV","SOM","SRB","SSD","STP","SUR","SVK","SVN","SWE","SWZ","SYC","SYR","TCD","TGO","THA","TJK","TKM","TLS","TON","TTO","TUN","TUR","TZA","UGA","UKR","URY","USA","UZB","VCT","VEN","VIR","VNM","VUT","PSE","WSM","YEM","ZAF","COD","ZMB","ZWE")
Regions_2012_Dataset <- c("The Americas","Asia","Africa","Europe","Middle East","The Americas","Asia","The Americas","Oceania","Europe","Asia","Africa","Europe","Africa","Africa","Asia","Europe","Middle East","The Americas","Europe","Europe","The Americas","The Americas","The Americas","The Americas","The Americas","Asia","Asia","Africa","Africa","The Americas","Europe","The Americas","Asia","Africa","Africa","Africa","The Americas","Africa","Africa","The Americas","The Americas","The Americas","Europe","Europe","Europe","Africa","Europe","The Americas","Africa","The Americas","Africa","Africa","Europe","Europe","Africa","Europe","Oceania","Europe","Oceania","Africa","Europe","Asia","Africa","Africa","Africa","Africa","Africa","Europe","The Americas","The Americas","The Americas","Oceania","The Americas","Asia","The Americas","Europe","The Americas","Europe","Asia","Asia","Europe","Middle East","Middle East","Europe","Middle East","Europe","The Americas","Middle East","Asia","Asia","Africa","Asia","Asia","Oceania","Asia","Middle East","Asia","Middle East","Africa","Africa","The Americas","Europe","Asia","Africa","Europe","Europe","Europe","Asia","Africa","Europe","Africa","Asia","The Americas","Europe","Africa","Europe","Asia","Europe","Asia","Africa","Africa","Africa","Africa","Asia","Africa","Oceania","Africa","Africa","The Americas","Europe","Europe","Asia","Oceania","Middle East","Asia","The Americas","The Americas","Asia","Oceania","Europe","The Americas","Europe","The Americas","Oceania","Middle East","Europe","Europe","Africa","Middle East","Africa","Africa","Asia","Oceania","Africa","The Americas","Africa","Europe","Africa","Africa","The Americas","Europe","Europe","Europe","Africa","Africa","Middle East","Africa","Africa","Asia","Asia","Asia","Asia","Oceania","The Americas","Africa","Europe","Africa","Africa","Europe","The Americas","The Americas","Asia","The Americas","The Americas","The Americas","Asia","Oceania","Middle East","Oceania","Middle East","Africa","Africa","Africa","Africa")

# Creating data frame
mydf <- data.frame(Country=Countries_2012_Dataset, Code=Codes_2012_Dataset, Region=Regions_2012_Dataset)
head(mydf)
tail(mydf)
summary(mydf)

# Merging data frames
merged <- merge(stats, mydf, by.x = "Country.Code", by.y = "Code")
head(merged)
merged$country <- NULL
str(merged)

# Visualizing with new split
qplot(data=merged, x=Internet.users, y=Birth.rate, colour=Region, size=I(5), shape=I(19), alpha=I(0.6), main="Birth Rate vs Internet Users")
      
```

# Scatter plot depicting life expectancy (y-axis) and fertility rate (x-axis) statistics by country and categorized by countries' regions
```{r}
# Data is provided for 2 years: 1960 and 2013 and a visualization needs to be provided for each year

#Execute below code to generate three new vectors
Country_Code <- c("ABW","AFG","AGO","ALB","ARE","ARG","ARM","ATG","AUS","AUT","AZE","BDI","BEL","BEN","BFA","BGD","BGR","BHR","BHS","BIH","BLR","BLZ","BOL","BRA","BRB","BRN","BTN","BWA","CAF","CAN","CHE","CHL","CHN","CIV","CMR","COG","COL","COM","CPV","CRI","CUB","CYP","CZE","DEU","DJI","DNK","DOM","DZA","ECU","EGY","ERI","ESP","EST","ETH","FIN","FJI","FRA","FSM","GAB","GBR","GEO","GHA","GIN","GMB","GNB","GNQ","GRC","GRD","GTM","GUM","GUY","HKG","HND","HRV","HTI","HUN","IDN","IND","IRL","IRN","IRQ","ISL","ITA","JAM","JOR","JPN","KAZ","KEN","KGZ","KHM","KIR","KOR","KWT","LAO","LBN","LBR","LBY","LCA","LKA","LSO","LTU","LUX","LVA","MAC","MAR","MDA","MDG","MDV","MEX","MKD","MLI","MLT","MMR","MNE","MNG","MOZ","MRT","MUS","MWI","MYS","NAM","NCL","NER","NGA","NIC","NLD","NOR","NPL","NZL","OMN","PAK","PAN","PER","PHL","PNG","POL","PRI","PRT","PRY","PYF","QAT","ROU","RUS","RWA","SAU","SDN","SEN","SGP","SLB","SLE","SLV","SOM","SSD","STP","SUR","SVK","SVN","SWE","SWZ","SYR","TCD","TGO","THA","TJK","TKM","TLS","TON","TTO","TUN","TUR","TZA","UGA","UKR","URY","USA","UZB","VCT","VEN","VIR","VNM","VUT","WSM","YEM","ZAF","COD","ZMB","ZWE")
Life_Expectancy_At_Birth_1960 <- c(65.5693658536586,32.328512195122,32.9848292682927,62.2543658536585,52.2432195121951,65.2155365853659,65.8634634146342,61.7827317073171,70.8170731707317,68.5856097560976,60.836243902439,41.2360487804878,69.7019512195122,37.2782682926829,34.4779024390244,45.8293170731707,69.2475609756098,52.0893658536585,62.7290487804878,60.2762195121951,67.7080975609756,59.9613658536585,42.1183170731707,54.2054634146342,60.7380487804878,62.5003658536585,32.3593658536585,50.5477317073171,36.4826341463415,71.1331707317073,71.3134146341463,57.4582926829268,43.4658048780488,36.8724146341463,41.523756097561,48.5816341463415,56.716756097561,41.4424390243903,48.8564146341463,60.5761951219512,63.9046585365854,69.5939268292683,70.3487804878049,69.3129512195122,44.0212682926829,72.1765853658537,51.8452682926829,46.1351219512195,53.215,48.0137073170732,37.3629024390244,69.1092682926829,67.9059756097561,38.4057073170732,68.819756097561,55.9584878048781,69.8682926829268,57.5865853658537,39.5701219512195,71.1268292682927,63.4318536585366,45.8314634146342,34.8863902439024,32.0422195121951,37.8404390243902,36.7330487804878,68.1639024390244,59.8159268292683,45.5316341463415,61.2263414634146,60.2787317073171,66.9997073170732,46.2883170731707,64.6086585365854,42.1000975609756,68.0031707317073,48.6403170731707,41.1719512195122,69.691756097561,44.945512195122,48.0306829268293,73.4286585365854,69.1239024390244,64.1918292682927,52.6852682926829,67.6660975609756,58.3675853658537,46.3624146341463,56.1280731707317,41.2320243902439,49.2159756097561,53.0013170731707,60.3479512195122,43.2044634146342,63.2801219512195,34.7831707317073,42.6411951219512,57.303756097561,59.7471463414634,46.5107073170732,69.8473170731707,68.4463902439024,69.7868292682927,64.6609268292683,48.4466341463415,61.8127804878049,39.9746829268293,37.2686341463415,57.0656341463415,60.6228048780488,28.2116097560976,67.6017804878049,42.7363902439024,63.7056097560976,48.3688048780488,35.0037073170732,43.4830975609756,58.7452195121951,37.7736341463415,59.4753414634146,46.8803902439024,58.6390243902439,35.5150487804878,37.1829512195122,46.9988292682927,73.3926829268293,73.549756097561,35.1708292682927,71.2365853658537,42.6670731707317,45.2904634146342,60.8817073170732,47.6915853658537,57.8119268292683,38.462243902439,67.6804878048781,68.7196097560976,62.8089268292683,63.7937073170732,56.3570487804878,61.2060731707317,65.6424390243903,66.0552926829268,42.2492926829268,45.6662682926829,48.1876341463415,38.206,65.6598292682927,49.3817073170732,30.3315365853659,49.9479268292683,36.9658780487805,31.6767073170732,50.4513658536585,59.6801219512195,69.9759268292683,68.9780487804878,73.0056097560976,44.2337804878049,52.768243902439,38.0161219512195,40.2728292682927,54.6993170731707,56.1535365853659,54.4586829268293,33.7271219512195,61.3645365853659,62.6575853658537,42.009756097561,45.3844146341463,43.6538780487805,43.9835609756098,68.2995365853659,67.8963902439025,69.7707317073171,58.8855365853659,57.7238780487805,59.2851219512195,63.7302195121951,59.0670243902439,46.4874878048781,49.969512195122,34.3638048780488,49.0362926829268,41.0180487804878,45.1098048780488,51.5424634146342)
Life_Expectancy_At_Birth_2013 <- c(75.3286585365854,60.0282682926829,51.8661707317073,77.537243902439,77.1956341463415,75.9860975609756,74.5613658536585,75.7786585365854,82.1975609756098,80.890243902439,70.6931463414634,56.2516097560976,80.3853658536585,59.3120243902439,58.2406341463415,71.245243902439,74.4658536585366,76.5459512195122,75.0735365853659,76.2769268292683,72.4707317073171,69.9820487804878,67.9134390243903,74.1224390243903,75.3339512195122,78.5466585365854,69.1029268292683,64.3608048780488,49.8798780487805,81.4011219512195,82.7487804878049,81.1979268292683,75.3530243902439,51.2084634146342,55.0418048780488,61.6663902439024,73.8097317073171,62.9321707317073,72.9723658536585,79.2252195121951,79.2563902439025,79.9497804878049,78.2780487804878,81.0439024390244,61.6864634146342,80.3024390243903,73.3199024390244,74.5689512195122,75.648512195122,70.9257804878049,63.1778780487805,82.4268292682927,76.4243902439025,63.4421951219512,80.8317073170732,69.9179268292683,81.9682926829268,68.9733902439024,63.8435853658537,80.9560975609756,74.079512195122,61.1420731707317,58.216487804878,59.9992682926829,54.8384146341464,57.2908292682927,80.6341463414634,73.1935609756098,71.4863902439024,78.872512195122,66.3100243902439,83.8317073170732,72.9428536585366,77.1268292682927,62.4011463414634,75.2682926829268,68.7046097560976,67.6604146341463,81.0439024390244,75.1259756097561,69.4716829268293,83.1170731707317,82.290243902439,73.4689268292683,73.9014146341463,83.3319512195122,70.45,60.9537804878049,70.2024390243902,67.7720487804878,65.7665853658537,81.459756097561,74.462756097561,65.687243902439,80.1288780487805,60.5203902439024,71.6576829268293,74.9127073170732,74.2402926829268,49.3314634146342,74.1634146341464,81.7975609756098,73.9804878048781,80.3391463414634,73.7090487804878,68.811512195122,64.6739024390244,76.6026097560976,76.5326585365854,75.1870487804878,57.5351951219512,80.7463414634146,65.6540975609756,74.7583658536585,69.0618048780488,54.641512195122,62.8027073170732,74.46,61.466,74.567512195122,64.3438780487805,77.1219512195122,60.8281463414634,52.4421463414634,74.514756097561,81.1048780487805,81.4512195121951,69.222,81.4073170731707,76.8410487804878,65.9636829268293,77.4192195121951,74.2838536585366,68.1315609756097,62.4491707317073,76.8487804878049,78.7111951219512,80.3731707317073,72.7991707317073,76.3340731707317,78.4184878048781,74.4634146341463,71.0731707317073,63.3948292682927,74.1776341463415,63.1670487804878,65.878756097561,82.3463414634146,67.7189268292683,50.3631219512195,72.4981463414634,55.0230243902439,55.2209024390244,66.259512195122,70.99,76.2609756097561,80.2780487804878,81.7048780487805,48.9379268292683,74.7157804878049,51.1914878048781,59.1323658536585,74.2469268292683,69.4001707317073,65.4565609756098,67.5223658536585,72.6403414634147,70.3052926829268,73.6463414634147,75.1759512195122,64.2918292682927,57.7676829268293,71.159512195122,76.8361951219512,78.8414634146341,68.2275853658537,72.8108780487805,74.0744146341464,79.6243902439024,75.756487804878,71.669243902439,73.2503902439024,63.583512195122,56.7365853658537,58.2719268292683,59.2373658536585,55.633)

# Data import
data <- read.csv(choose.files())

#Explore the data
data
head(data)      #check top 6 rows
tail(data, rows=7) #check bottom 7 rows
str(data)      #check the structure of the data frame
summary(data)      #check the summary of the data

#Did you pick up that there is more than one year in the data?
#From the challenge we know that there are two: 1960 and 2013

#Filter the dataframes
data1960 <- data[data$Year==1960,]
data2013 <- data[data$Year==2013,]

#Check row counts
nrow(data1960) #187 rows
nrow(data2013) #187 rows. Equal split.

#Create the additional dataframes
add1960 <- data.frame(Code=Country_Code, Life.Exp=Life_Expectancy_At_Birth_1960)
add2013 <- data.frame(Code=Country_Code, Life.Exp=Life_Expectancy_At_Birth_2013)

#Check summaries
summary(add1960)
summary(add2013)

#Merge the pairs of dataframes  
merged1960 <- merge(data1960, add1960, by.x="Country.Code", by.y="Code")
merged2013 <- merge(data2013, add2013, by.x="Country.Code", by.y="Code")

#Check the new structures
str(merged1960)
str(merged2013)

#We can see an obsolete column in each of the merged dataframes
#Column "Year" is no longer required. Let's remove it
merged1960$Year <- NULL
merged2013$Year <- NULL

#Check structures again
str(merged1960)
str(merged2013)

#Visualization time
library(ggplot2)

#Visualize the 1960 dataset
qplot(data=merged1960, x=Fertility.Rate, y=Life.Exp,
      color=Region,                               #colour
      size=I(5), 
      alpha=I(0.6),                               #transparency
      main="Life Expectancy vs Fertility (1960)" #title
   )

#Visualize the 2013 dataset
qplot(data=merged2013, x=Fertility.Rate, y=Life.Exp,
      color=Region,
      size=I(5),
      alpha=I(0.6),
      main="Life Expentancy vs Fertility (2013)"
      )

```
# Advanced visualizations using ggplot2
```{r}
movies <- read.csv(file.choose())
head(movies)
colnames(movies) <- c("Film", "Genre", "CriticRating", "AudienceRating", "BudgetMillions", "Year")
head(movies)
tail(movies)
str(movies)
factor(movies$Year)
summary(movies)
str(movies)

library(ggplot2)
q <- ggplot(data=movies, aes(x=CriticRating, y=AudienceRating, colour=Genre, size=BudgetMillions)) +
geom_point()

q + geom_point(aes(size=CriticRating)) # Overriding aes

q + geom_point(aes(x=BudgetMillions)) +
  xlab("Budget Millions $$$")

q + geom_line(size=1)

q + geom_point(colour="DarkGreen") # Set the color. Don't use aes

q + geom_point(aes(size=BudgetMillions)) # Mapping

q + geom_point(size=10) # Setting

# Histogram
s <- ggplot(data=movies, aes(x=BudgetMillions))
s + geom_histogram(binwidth=10, aes(fill=Genre), colour="Black")

# Density chart
s + geom_density(aes(fill=Genre), position="stack")

# Layers
t <- ggplot(data=movies)
t + geom_histogram(binwidth=10, 
                   aes(x=AudienceRating),
                   fill="White", colour="Blue")

# geom_smooth
u <- ggplot(data=movies, aes(x=CriticRating, y=AudienceRating,
                             colour=Genre))
u + geom_point() + geom_smooth(fill=NA)

# Boxplots
u <- ggplot(data=movies, aes(x=Genre, y=AudienceRating,
            colour=Genre))
u + geom_boxplot(size=1.2)

# Using facets
library(ggplot2)
# Histogram and facets
v <- ggplot(data=movies, aes(x=BudgetMillions))
v + geom_histogram(binwidth=10, aes(fill=Genre),
                   colour="Black") +
  facet_grid(Genre~., scales="free")

# scatterplots and facets
w <- ggplot(data=movies, aes(x=CriticRating, y=AudienceRating,
                             colour=Genre))
w + geom_point(size=3) + 
  facet_grid(Genre~.)

w + geom_point(aes(size=BudgetMillions)) +
  geom_smooth(fill=NA) +
  facet_grid(Genre~Year)

# Coordinate
# Limits
m <- ggplot(data=movies, aes(CriticRating, y=AudienceRating,
                             size=BudgetMillions,
                             colour=Genre))
m + geom_point()
m + geom_point() +
  xlim(50,100) +
  ylim(50,100)
# Doesn't always work well
n <- ggplot(data=movies, aes(x=BudgetMillions))
n + geom_histogram(binwidth = 10, aes(fill=Genre), colour="Black") +
  ylim(0,50)

# Instead zoom
n + geom_histogram(binwidth = 10, aes(fill=Genre), colour="Black") +
  coord_cartesian(ylim = c(0,50))
 
w + geom_point(aes(size=BudgetMillions)) +
  geom_smooth(fill=NA) +
  facet_grid(Genre~Year) +
  coord_cartesian(ylim = c(0,100))

# Adding a theme
o <- ggplot(data=movies, aes(x=BudgetMillions))
h <- o + geom_histogram(binwidth = 10, aes(fill=Genre), colour="Black")
h + xlab("Money Axis") +
  ylab("Number of Movies") +
  ggtitle("Movie Budget Distribution") +
  theme(axis.title.x = element_text(colour = "DarkGreen", size = 30), axis.title.y = element_text(colour = "Red", size = 30),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        legend.title = element_text(size = 30),
        legend.text = element_text(size = 20),
        legend.position = c(1,1),
        legend.justification = c(1,1),
        plot.title = element_text(colour = "DarkBlue",
                                  size=40))


mov <- read.csv(file.choose())
#Data Exploration
head(mov) #top rows
summary(mov) #column summaries
str(mov) #structure of the dataset

#Activate GGPlot2
#install.packages("ggplot2")
library(ggplot2)
#install.packages("extrafont")
library(extrafont) 
font_import()
loadfonts(device = "win")
#{Offtopic} This Is A Cool Insight:
ggplot(data=mov, aes(x=Day.of.Week)) + geom_bar()
#Notice? No movies are released on a Monday. Ever.

#Now we need to filter our dataset to leave only the 
#Genres and Studios that we are interested in
#We will start with the Genre filter and use the Logical 'OR'
#operator to select multiple Genres:
filt <- (mov$Genre == "action") | (mov$Genre == "adventure") | (mov$Genre == "animation") | (mov$Genre == "comedy") | (mov$Genre == "drama")

#Now let's do the same for the Studio filter:
filt2 <- (mov$Studio == "Buena Vista Studios") | (mov$Studio == "WB") | (mov$Studio == "Fox") | (mov$Studio == "Universal") | (mov$Studio == "Sony") | (mov$Studio == "Paramount Pictures")
  
#Apply the row filters to the dataframe
mov2 <- mov[filt & filt2,]

#Prepare the plot's data and aes layers
#Note we did not rename the columns. 
#Use str() or summary() to fin out the correct column names
p <- ggplot(data=mov2, aes(x=Genre, y=Gross...US))
p #Nothing happens. We need a geom.

#Add a Point Geom Layer
p + 
  geom_point()

#Add a boxplot instead of the points
p + 
  geom_boxplot()

#Notice that outliers are part of the boxplot layer
#We will use this observation later (*)

#Add points
p + 
  geom_jitter()
  
  
#Not what we are after

#Replace points with jitter
p + 
  geom_jitter() + 
  geom_boxplot(alpha=0.7) 


#Good. Now add size and colour to the points:
p + 
  geom_jitter(aes(size=Budget...mill., colour=Studio)) + 
  geom_boxplot(alpha=0.7) 
#See the remaining black points? Where are they from?
#They are part of the boxplot - Refer to our observation (*) above 

#Let's remove them:
p + 
  geom_jitter(aes(size=Budget...mill., colour=Studio)) + 
  geom_boxplot(alpha = 0.7, outlier.colour = NA) 

#Let's "Save" our progress by placing it into a new object:
q <- p + 
  geom_jitter(aes(size=Budget...mill., colour=Studio)) + 
  geom_boxplot(alpha = 0.7, outlier.colour = NA) 
q

#Non-data ink
q <- q +
  xlab("Genre") + #x axis title
  ylab("Gross % US") + #y axis title
  ggtitle("Domestic Gross % by Genre") #plot title
q

#HINT: for the next part use ?theme if you need to 
#refresh which parameters are responsible for what

#Theme
q <- q + 
  theme(
    axis.title.x = element_text(colour = "Blue", size = 30),
    axis.title.y = element_text(colour = "Blue", size = 30),
    axis.text.x = element_text(size = 20),
    axis.text.y = element_text(size = 20),
    plot.title = element_text(size = 40),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 20),
   
  )
 q   
  
#Final touch. We haven't discussed this in the course,
#However this is how you can change individual legend titles:
q$labels$size <- "Budget $M"
q

```

# loops
```{r}
df <- data.frame(a = c(1:10), b = c(11:20))
df
myFunc <- function(x,y){
  x*y
}
for(i in 1:nrow(df)){
  temp <- myFunc(df[i,"a"], df[i, "b"])
  if(temp>100){
    print (c(i, temp))
  }
}

```
```{r}
df <- data.frame(a = c(1:10), b = c(11:20))
myFunc <- function(x,y){
  x*y
}
sodi <- function(j){
 11-j 
}
for(i in 1:nrow(df)){
  temp <- myFunc(df[i,"a"], df[sodi(i), "b"])
  print (c(i, temp))
}
```
```{r}
for(i in 0:3)
{
  cat(i, "\n")
}
```
```{r}
x = c(1,3,4,7)
x
n = length(x)
for(i in 1:n)
{
  x[i] = x[i] = i
}
```
```{r}
n = 4
a = 1
for(i in 1:n)
{
  a[i+1] = 2*a[i]
}
```

```{r}
for(i in 1:7)
{
print(i^3) 
}
```
```{r}
for(i in 1:10)
{
  x1 <- i^2
  print(x1)
}
```
```{r}
x2 <- c("Max", "Tina", "Lindsey", "Anton", "Sharon")
{
  for(i in x2)
  print(paste("The name", i, "consists of", nchar(i), "characters."))
}
```
```{r}
for(i in names(iris)){
  print(paste0(i, " (", nchar(i), ")"))
}

```
```{r}
while(TRUE)
{
  x <- rnorm(1)
  if(x < 0) {
    next
    }
  print(x)
  if(x > 1){
    break
  }
}
```
```{r}
n <- 20
sedi <- c(0L, 1L)
coin_outc <- vector(length = n, mode = "integer")
for(i in 1:n){
  coin_outc[i] <- sample(sedi, 1)
}
coin_outc
```
```{r}
mat <- matrix(NA_integer_, nrow = 5, ncol = 5)
for(i in 1:5){
  for(j in 1:5){
    mat[i, j] <- abs(i - j)
  }
}
mat
```
```{r}
x <- c(-3,6,2,5,9)
for(i in x){
  print(c(i, i^2))
}
```
```{r}
storage <- c(1:5)
for(i in 1:5){
  storage[i] <- i^2
}
storage
```
```{r}
x <- c(-3,6,2,5,9)
x
storage2 <- numeric(5)
storage2
for(in in storage2){
  storage2[i] <- (x[i])i^2
}
storage2
```
```{r}
for(DegC in c(-3,6,2,5,9)){
  DegF <- DegC*(9/5)+32
  print(c(DegC,DegF))
}
```
```{r}
for(Temp in c(-4,5,10,-6,-40,30)){
  if(Temp>0){
    print("warm")
  } else {
    print("not so warm")
  }
}
```
```{r}
for(i in 1:3){
for(j in 1:2){
  print(i + j)
}
}
```
```{r}
x<-1
while(x<10){
  print(x)
  x<-x+1
}
```
```{r}
i<-1
while(i<=2){
  j<-1
  while(j<=2){
    print(c(i,j))
    j<-j+1
  }
    i<-i+1
}
```

```{r}
x<-1
while(x<2){
  print(x)
  x
}
```

```{r}
n <- 20
myvec <- c(head=0L, tail=1L)
coin <- vector(length = n, mode = "integer")
for(i in 1:n){
  coin[i] <- sample(myvec, 1)
}
coin

```